The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-18 paper/main.tex
Removed the date.
Added a CTS2 citation.

\date{}

@@

As a case study, the CTS2 OMG\textregistered  Specification\footnote{https://github.com/cts2/cts2-specification} used GitHub issue tracker to track specification changes. Elicitation, Analysis and Negotiation were natural fits for the issue tracker. This was chosen in part because the barrier to participation was very small (only a GitHub account was needed), and issues tracker itself allowed for dialogs in the form of comments. Because customer involvement is critical to these activities\cite{paetsch2003requirements}, ease of contribution was a main concern. OMG has a predescribed format for requirements Documentation, but using the GitHub issue API\footnote{http://developer.github.com/v3/issues/}, much of this documentation can be automated.
Validation and Management are areas of requirements engineering that GitHub has interesting solutions for. First, in order to track (or validate) changes to the specification, when the actual specification is modified, the commit that modified it can be traced to a named issue by simply putting the issue number in the commit log. This level of traceability is powerful, as it allows every change to the specification artifacts to be tracked consistently to an open issue. As the normal OMG process proceeds, requirements can be managed through ``tagging'' the issues. By allowing issues to be grouped by arbitrary tags, users are more free to adapt their own workflow. For instance, when community voting on issues needed to be done for CTS2, a simple ``ready for vote'' tag signified to the voting board exactly what was under consideration.

>>>>

@@

As a case study, the CTS2 OMG\textregistered Specification\cite{cts2} used a GitHub issue tracker\footnote{https://github.com/cts2/cts2-specification/issues} to track specification changes. Elicitation, Analysis and Negotiation were natural fits for the issue tracker. This was chosen in part because the barrier to participation was very small (only a GitHub account was needed), and issues tracker itself allowed for dialogs in the form of comments. Because customer involvement is critical to these activities\cite{paetsch2003requirements}, ease of contribution was a main concern. OMG has a predescribed format for requirements Documentation, but using the GitHub issue API\footnote{http://developer.github.com/v3/issues/}, much of this documentation can be automated.
Validation and Management are areas of requirements engineering that GitHub has interesting solutions for. First, in order to track (or validate) changes to the specification, when the actual specification is modified, the commit that modified it can be traced to a named issue by simply putting the issue number in the commit log. This level of traceability is powerful, as it allows every change to the specification artifacts to be tracked consistently to an open issue. As the normal OMG process proceeds, requirements can be managed through ``tagging'' the issues. By allowing issues to be grouped by arbitrary tags, users are more free to adapt their own workflow. For instance, when community voting on issues needed to be done for CTS2, a simple ``ready for vote'' tag signified to the voting board exactly what was under consideration.
